\bibitem{idc} (2015, Jun) ``Internet of Things Market to Reach \$1.7 Trillion by 2020''. The Wall Street Journal. Available: https://blogs.wsj.com/cio/2015/06/02/internet-of-things-market-to-reach-1-7-trillion-by-2020-idc/ (Accessed Oct 25, 2017)
\bibitem{davies} Davies, Nigel, et al. ``Privacy mediators: Helping iot cross the chasm.'' Proceedings of the 17th International Workshop on Mobile Computing Systems and Applications. ACM, 2016.
\bibitem{campbell} Hashemi, Sayed Hadi, et al. ``World of Empowered IoT Users.'' Internet-of-Things Design and Implementation (IoTDI), 2016 IEEE First International Conference on. IEEE, 2016.
\bibitem{zhang} Zhang, Nan, et al. ``Understanding IoT Security Through the Data Crystal Ball: Where We Are Now and Where We Are Going to Be.'' arXiv preprint arXiv:1703.09809. arXiv, 2017
\bibitem{statcount} (2016, Nov.) ``Mobile and tablet internet usage exceeds desktop for first time worldwide.'' Statcounter global stats. [Online]. Available: http://gs.statcounter.com/press/mobile-and-tablet-internet-usage-exceeds-desktop-for-first-time-worldwide (Accessed Oct 24, 2017)
\bibitem{tz} Ahmed M. Azab, et al. 2014. ``Hypervision Across Worlds: Real-time Kernel Protection from the ARM TrustZone Secure World.'' In Proceedings of the 2014 ACM SIGSAC Conference on Computer and Communications Security (CCS '14). ACM, New York, NY, USA, 90-102. DOI: http://dx.doi.org/10.1145/2660267.2660350
\bibitem{leaky} Wang, Wenhao, et al. ``Leaky Cauldron on the Dark Land: Understanding Memory Side-Channel Hazards in SGX.'' ACM Computer and Communications Security (CCS ’17), October, 2017.
\bibitem{mengjia} Yan, Mengjia, et al. 2017. ``Secure Hierarchy-Aware Cache Replacement Policy (SHARP): Defending Against Cache-Based Side Channel Atacks.'' In Proceedings of the 44th Annual International Symposium on Computer Architecture (ISCA '17). ACM, New York, NY, USA, 347-360. DOI: https://doi.org/10.1145/3079856.3080222
\bibitem{raccoon} Rane, Ashay, et al. ``Raccoon: Closing digital side-channels through obfuscated execution.'' In USENIX Security Symposium (2015).
\bibitem{atzori} Atzori, Luigi, Antonio Iera, and Giacomo Morabito. ``The internet of things: A survey." Computer networks 54.15 (2010): 2787-2805.
\bibitem{itu} (2012, Jun) ``Overview of Internet of Things.'' ITU-T Recommendations. Available: http://www.itu.int/ITU-T/recommendations/rec.aspx?rec=y.2060 (Accessed Oct 25, 2017)
\bibitem{enclave} Costan, Victor, et al. ``Intel SGX Explained.'' IACR Cryptology ePrint Archive 2016 (2016): 86.
\bibitem{rico} Deka, Biplab, et al. 2017. ``Rico: A Mobile App Dataset for Building Data-Driven Design Applications.'' In Proceedings of the 30th Annual Symposium on User Interface Software and Technology (UIST '17).
\bibitem{smartthings} E. Fernandes, J. Jung and A. Prakash. ``Security Analysis of Emerging Smart Home Applications." 2016 IEEE Symposium on Security and Privacy (SP) (2016).
\bibitem{idc_android} ``Smartphone OS Market Share, 2017 Q1''. idc.com. Available: https://www.idc.com/promo/smartphone-market-share/os (Accessed Dec 14, 2017)
\bibitem{mturk} ``Amazon mechanical turk - Business feedback''. Amazon mechanical turk - Requester. Available: https://requester.mturk.com/tour/business\_feedback (Accessed Dec 14, 2017)
